Logsums

### 2020-04-27 04_accessibility.Rmd
Add distance check graphic
This check reveals plenty of inconsistencies with the blockgroup-based shortest distance calculations

```{r distance_adjust}
distance_files <- list.files("data/nyc_shortest_paths_3500m/", full.names = TRUE)

read_all_files <- function(pattern = pattern, path = "./"){
  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
         col_types = list(geoid = col_character(), park_id = col_character()))
}
distances <- read_all_files(".csv", "data/nyc_shortest_paths_5000m/") %>%
  # filter out infinite paths
  filter(!is.infinite(distance)) %>%
  # add ten meters to all paths
  mutate(distance = distance + 10)
```

>>>>

```{r distance_adjust}
read_all_files <- function(pattern = pattern, path = "./"){
  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
         col_types = list(geoid = col_character(), park_id = col_character()))
}
distances <- read_all_files(".csv", "data/nyc_shortest_paths_5000m/") %>%
  # filter out infinite paths
  filter(!is.infinite(distance)) %>%
  # add ten meters to all paths
  mutate(distance = distance + 10)
```

```{r check-distances}
check_id = "M010"
check <- bg_poly %>%
  left_join(distances %>% filter(park_id == check_id), by = "geoid") %>%
  mutate(distance = log(distance + 10)) %>% 
  st_transform(4326)
park <- open_spaces %>% st_transform(4326) %>% filter(id == check_id)

pal <- colorNumeric("plasma", check$distance)
leaflet(check ) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(color = ~pal(distance) ) %>%
  addPolygons(data = park, color = "green")
```
